### 2024-10-02 Notes/Notes.tex
Contacts update
Contacts.md creation
Creation of the ChEMBL_ExtractorData

@@

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{reflection}{Reflection}
\newtheorem{book}{Book}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% CONTACTS %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Contacts}
IIIA (Institut d'Investigació en Inteligència Artificial): 
\begin{itemize}
\item General consultes \href{tel:93 580 9570}{+34 93 580 9570}
\item \href{https://www.iiia.csic.es/en-us/people/person/?person_id=39}{Pablo Noriega}: \href{mailto:pablo@iiia.csic.es}{pablo@iiia.csic.es}
\end{itemize}
Chemistry department - UAB
\begin{itemize}
\item General consultes \href{tel:93 580 9570}{+34 93 580 9570}
\item \href{https://www.iiia.csic.es/en-us/people/person/?person_id=39}{Pablo Noriega}: \href{mailto:pablo@iiia.csic.es}{pablo@iiia.csic.es}
\end{itemize}

@@

>>>>

%%%%%%%%%%%%%%% CODELISTINGS %%%%%%%%%%%%%%%%
\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=t,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{reflection}{Reflection}
\newtheorem{PyPackage}{Package}
\newtheorem{book}{Book}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Packages}

\begin{PyPackage}
"Requests allows you to send HTTP/1.1 requests extremely easily. There’s no need to manually add query strings to your URLs, or to form-encode your POST data. Keep-alive and HTTP connection pooling are 100\% automatic, thanks to urllib3."
\cite{PythonPackageRequests}. We will use this package to create requests to the ChEMBL database.
\end{PyPackage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% BOOKS %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% VARIOUS %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Various}

\begin{lstlisting}[language=C, caption=Example of a JSON file.]
{
  "page_meta": {
    "limit": 1000,
    "offset": 0,
    "total_count": 1500,
    "next": "/chembl/api/data/activity.json?limit=1000&offset=1000&target_chembl_id=CHEMBL372&standard_type=IC50",
    "previous": null
  },
  "activities": [
    {
      "activity_id": 123456789,
      "assay_chembl_id": "CHEMBL123456",
      "molecule_chembl_id": "CHEMBL25",
      "canonical_smiles": "CCOCCO",
      "standard_value": "50",
      "standard_units": "nM",
      "standard_type": "IC50",
      "target_chembl_id": "CHEMBL372",
      "assay_type": "B",
      "relation": "=",
      "document_chembl_id": "CHEMBL12345"
    },
    {
      "activity_id": 987654321,
      "assay_chembl_id": "CHEMBL654321",
      "molecule_chembl_id": "CHEMBL1095",
      "canonical_smiles": "CCCN(CC)CC",
      "standard_value": "25",
      "standard_units": "nM",
      "standard_type": "IC50",
      "target_chembl_id": "CHEMBL372",
      "assay_type": "B",
      "relation": "<",
      "document_chembl_id": "CHEMBL54321"
    }
    // More activity entries...
  ]
}
\end{lstlisting}
